---
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  pdf_document: default
  word_document: default
  html_document: default
---


```{r setup, include=FALSE}
## Setting the WD this way will prevent the need for everyone to have specific code for their own computers.

library(stringr)
library(lubridate)

## WORKING DIRECTORY 
current_wd <- getwd()

if(grepl("keshetronen", current_wd)) {
  workingdir <- "/Users/keshetronen/Library/CloudStorage/OneDrive-SharedLibraries-UW/Arya Kadakia - PCORI/DataTables"
} else if(grepl("arya", current_wd)){
  workingdir <- "C:/Users/arya1999/OneDrive - UW/PCORI/DataTables"
} else {
  print("Incorrect working directory.")
}

## GENERATE DATE OF CLOSEST FRIDAY (IF TODAY IS FRIDAY, IT WILL RETURN TODAY'S DATE)
last_friday <- Sys.Date() - wday(Sys.Date() + 1)

if((Sys.Date()-last_friday)>=7){
  last_friday <- Sys.Date()
}

```

---
title: "PCORI data report"
author: "Keshet Ronen & Arya Kadakia"
date: "Report run with data up to `r last_friday`"
output:
  pdf_document: default
  word_document: default
---

\newpage
```{r knitr, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.width = 7, fig.height = 9, fig.margin = c(1, 1, 1, 1, "in"))
```

```{r packages, include=FALSE}

packages <- c("redcapAPI", "dplyr","magrittr","zoo","lubridate","ggplot2","openxlsx", "png","knitr","DiagrammeR", "tidyverse", "eeptools", "stringr", "haven", "reshape2", "here", "Hmisc", "anthro", "devtools", "kableExtra", "gdata", "compareGroups", "readxl", "foreign", "devtools", "httr", "table1", "readxl", "gtsummary", "chron")


devtools::install_github("kupietz/kableExtra")

for (val in packages){
lapply(packages, library, character.only = TRUE)
}

(.packages())


```

```{r data, include=FALSE}

## From Redcap 
screen <- read.csv(paste(workingdir,"/REDCapData/PCORIClientScreener_DATA_", last_friday, ".csv", sep=""))

assess <- read.csv(paste(workingdir,"/REDCapData/PCORIClientAssessmen_DATA_", last_friday, ".csv", sep=""))


## need to save LMS data as utf8 encoded (or find a way to change encoding in import)
#lms <- read.csv(paste(workingdir,"/LMSData/Weekly_Metrics_DATA_", last_friday, ".csv", sep=""))



```

```{r data_clean, include=FALSE}

# subset screening dataset to exclude records with duplicate phone numbers (keep 1st instance of duplicates)
invalid <- c("1")
screen_dedup <- screen[!(screen$track_invalid %in% invalid), ]

#Places for People
pfp_screen <- screen_dedup[screen_dedup$health_center == 1, ]
pfp_assess <- assess[grepl("^P", assess$redcap_survey_identifier), ]

#Manchester
mh_screen <- screen_dedup[screen_dedup$health_center == 2, ]
mh_assess <- assess[grepl("^M", assess$redcap_survey_identifier), ]

#Community Partners
cp_screen <- screen_dedup[screen_dedup$health_center == 3, ]
cp_assess <- assess[grepl("^C", assess$redcap_survey_identifier), ]


#last week calculations
screen_dedup$date <- as.Date(substr(screen_dedup$datetime,start = 1, stop = 10))
screen_dedup_lw <- screen_dedup %>% filter(date >= last_friday-7)

pfp_screen_lw <- screen_dedup_lw[screen_dedup_lw$health_center == 1, ]
mh_screen_lw <- screen_dedup_lw[screen_dedup_lw$health_center == 2, ]
cp_screen_lw <- screen_dedup_lw[screen_dedup_lw$health_center == 3, ]

###
pfp_call_date <- pfp_screen %>% filter(track_call_date >= last_friday-7)
mh_call_date <- mh_screen %>% filter(track_call_date >= last_friday-7)
cp_call_date <- cp_screen %>% filter(track_call_date >= last_friday-7)

####
assess$date <- as.Date(substr(assess$start_datetime,start = 1, stop = 10))
assess_lw <- assess %>% filter(date >= last_friday-7)

pfp_assess_lw <- assess_lw[grepl("^P", assess_lw$redcap_survey_identifier), ]
mh_assess_lw <- assess_lw[grepl("^M", assess_lw$redcap_survey_identifier), ]
cp_assess_lw <- assess_lw[grepl("^C", assess_lw$redcap_survey_identifier), ]
###

```
\newpage
## Updates Table

```{r Updates, echo=FALSE}
#referred

pfp_referred <- length(unique(pfp_screen$client_id))
mh_referred <- length(unique(mh_screen$client_id))
cp_referred <- length(unique(cp_screen$client_id))

pfp_referred_lw <-  length(unique(pfp_screen_lw$client_id))
mh_referred_lw <- length(unique(mh_screen_lw$client_id))
cp_referred_lw <- length(unique(cp_screen_lw$client_id))

# waiting to call
pfp_waiting <- pfp_referred - (sum(pfp_screen$track_consent_call==1, na.rm=T) + sum(pfp_screen$call_interest==0, na.rm=T))
mh_waiting <- mh_referred - sum(mh_screen$track_consent_call==1, na.rm=T) - sum(mh_screen$call_interest==0, na.rm=T)
cp_waiting <- cp_referred - (sum(cp_screen$track_consent_call==1, na.rm=T) + sum(cp_screen$call_interest==0, na.rm=T))

# not interested in study
pfp_no_interest <- sum(pfp_screen$call_interest==0 | pfp_screen$track_participation_type == 3, na.rm=T)
mh_no_interest <- sum(mh_screen$call_interest==0 | mh_screen$track_participation_type == 3, na.rm=T)
cp_no_interest <- sum(cp_screen$call_interest==0 | cp_screen$track_participation_type == 3, na.rm=T)

# interested in study
pfp_call <- sum(pfp_screen$track_participation_type==1, na.rm=T) + sum(pfp_screen$track_participation_type==2, na.rm=T)
mh_call <- sum(mh_screen$track_participation_type==1, na.rm=T) + sum(mh_screen$track_participation_type==2, na.rm=T)
cp_call <- sum(cp_screen$track_participation_type==1, na.rm=T) + sum(cp_screen$track_participation_type==2, na.rm=T)

pfp_call_lw <- sum(pfp_call_date$track_consent_call, na.rm = T)
mh_call_lw <- sum(mh_call_date$track_consent_call, na.rm = T)
cp_call_lw <- sum(cp_call_date$track_consent_call, na.rm = T)

#ineligible for FOCUS
pfp_focus_ineligible <- sum(pfp_screen$track_focus_eligible==0 & pfp_screen$track_participation_type!=3, na.rm = T)
mh_focus_ineligible <- sum(mh_screen$track_focus_eligible==0 & mh_screen$track_participation_type!=3, na.rm = T)
cp_focus_ineligible <- sum(cp_screen$track_focus_eligible==0 & cp_screen$track_participation_type!=3, na.rm = T)
 
# Using FOCUS only

pfp_focus_study_ineligible <- sum(pfp_screen$track_focus_study_ineligble, na.rm = TRUE)
mh_focus_study_ineligible <- sum(mh_screen$track_focus_study_ineligble, na.rm = TRUE)
cp_focus_study_ineligible <- sum(cp_screen$track_focus_study_ineligble, na.rm = TRUE)

pfp_focus_only_eligible <- sum(pfp_screen$track_focus_eligible[pfp_screen$track_participation_type == 2], na.rm = TRUE)
mh_focus_only_eligible <- sum(mh_screen$track_focus_eligible[mh_screen$track_participation_type == 2], na.rm = TRUE)
cp_focus_only_eligible <- sum(cp_screen$track_focus_eligible[cp_screen$track_participation_type == 2], na.rm = TRUE)

pfp_focus_only <- pfp_focus_study_ineligible + pfp_focus_only_eligible
mh_focus_only <- mh_focus_study_ineligible + mh_focus_only_eligible
cp_focus_only <- cp_focus_study_ineligible + cp_focus_only_eligible

## eligible for study?

# Consented to Study
pfp_consented <- sum(pfp_screen$track_obtained_consent, na.rm=T)
mh_consented <- sum(mh_screen$track_obtained_consent, na.rm=T)
cp_consented <- sum(cp_screen$track_obtained_consent, na.rm=T)

# Completed Baseline
pfp_baseline = sum(pfp_assess$track_survey_completion==1, na.rm=T)
mh_baseline = sum(mh_assess$track_survey_completion==1, na.rm=T)
cp_baseline = sum(cp_assess$track_survey_completion==1, na.rm=T)

pfp_baseline_lw = sum(pfp_assess_lw$track_survey_completion==1, na.rm=T)
mh_baseline_lw = sum(mh_assess_lw$track_survey_completion==1, na.rm=T)
cp_baseline_lw = sum(cp_assess_lw$track_survey_completion==1, na.rm=T)

# Lost to follow-up after baseline
pfp_lost_b = sum(pfp_assess$b_follow_lost==1, na.rm=T)
mh_lost_b = sum(mh_assess$b_follow_lost==1, na.rm=T)
cp_lost_b = sum(cp_assess$b_follow_lost==1, na.rm=T)

# Lost to follow-up after intervention
pfp_lost_m = sum(pfp_assess$m_follow_lost==1, na.rm=T)
mh_lost_m = sum(mh_assess$m_follow_lost==1, na.rm=T)
cp_lost_m = sum(cp_assess$m_follow_lost==1, na.rm=T)

#Installed FOCUS
pfp_install <- sum(pfp_screen$track_installed_focus, na.rm=T)
mh_install <- sum(mh_screen$track_installed_focus, na.rm=T)
cp_install <- sum(cp_screen$track_installed_focus, na.rm=T)

#Android:iPhone
pfp_android <- sum(pfp_screen$track_os == 1, na.rm = TRUE)
pfp_iphone <- sum(pfp_screen$track_os == 2, na.rm = TRUE)
pfp_os <- paste(pfp_android, ":", pfp_iphone, sep = "")

mh_android <- sum(mh_screen$track_os == 1, na.rm = TRUE)
mh_iphone <- sum(mh_screen$track_os == 2, na.rm = TRUE)
mh_os <- paste(mh_android, ":", mh_iphone, sep = "")

cp_android <- sum(cp_screen$track_os == 1, na.rm = TRUE)
cp_iphone <- sum(cp_screen$track_os == 2, na.rm = TRUE)
cp_os <- paste(cp_android, ":", cp_iphone, sep = "")

#Completed 3M
pfp_3m = sum(pfp_assess$track_survey_completion_v2==1, na.rm=T)
mh_3m = sum(mh_assess$track_survey_completion_v2==1, na.rm=T)
cp_3m = sum(cp_assess$track_survey_completion_v2==1, na.rm=T)

pfp_3m_lw = sum(pfp_assess_lw$track_survey_completion_v2==1, na.rm=T)
mh_3m_lw = sum(mh_assess_lw$track_survey_completion_v2==1, na.rm=T)
cp_3m_lw = sum(cp_assess_lw$track_survey_completion_v2==1, na.rm=T)


####

# Create a matrix with column names as row names
table_matrix <- matrix(
  c(
    paste(pfp_referred, " (+", pfp_referred_lw, ")", sep = ""), paste(mh_referred, " (+", mh_referred_lw, ")", sep = ""), paste(cp_referred, " (+", cp_referred_lw, ")", sep = ""),
    pfp_waiting,  mh_waiting, cp_waiting,
    pfp_no_interest, mh_no_interest, cp_no_interest, 
    paste(pfp_call, " (+", pfp_call_lw, ")", sep = ""), paste(mh_call, " (+", mh_call_lw, ")", sep = ""), paste(cp_call, " (+", cp_call_lw, ")", sep = ""), 
    pfp_focus_ineligible, mh_focus_ineligible, cp_focus_ineligible,
    pfp_focus_only, mh_focus_only, cp_focus_only,
    pfp_consented, mh_consented, cp_consented,
    paste(pfp_baseline, " (+", pfp_baseline_lw, ")", sep = ""), paste(mh_baseline, " (+", mh_baseline_lw, ")", sep = ""), paste(cp_baseline, " (+", cp_baseline_lw, ")", sep = ""), pfp_lost_b, mh_lost_b, cp_lost_b,
    pfp_install, mh_install, cp_install,
    pfp_os, mh_os, cp_os, pfp_lost_m, mh_lost_m, cp_lost_m,
    paste(pfp_3m, " (+", pfp_3m_lw, ")", sep = ""), paste(mh_3m, " (+", mh_3m_lw, ")", sep = ""), paste(cp_3m, " (+", cp_3m_lw, ")", sep = "")
  ),
  nrow = 13,
  byrow = TRUE
)

colnames(table_matrix) <- c("PfP", "MHCGM", "CP")
rownames(table_matrix) <- c("Referred", "Waiting to call", "Not interested", "Given info call", "Ineligible for FOCUS", "Using FOCUS only", "Consented to study", "Completed baseline", "Lost to follow-up (post baseline)", "Installed FOCUS", "Android:iPhone", "Lost to follow-up (post intervention)", "Completed 3M")

# Generate the table using kableExtra
library(kableExtra)
kable(table_matrix, format = "latex", booktabs = TRUE, escape = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage
## Duplicates List

```{r duplicates, echo=FALSE, comment=NA}

# all name lower case
screen_lower <- screen %>%
  mutate(client_first_name = tolower(client_first_name),
         client_last_name = tolower(client_last_name))

# Printing duplicates based on (client_first_name AND client_last_name) or phone
duplicates <- screen_lower[duplicated(screen_lower[c("client_first_name", "client_last_name")]) |
                 duplicated(screen_lower[c("client_first_name", "client_last_name")], fromLast = TRUE) |
                 duplicated(screen_lower$phone) | duplicated(screen_lower$phone, fromLast = TRUE), ]

reviewed <- c("1", "0")
dups <- duplicates[!(duplicates$track_invalid %in% reviewed),]

if (length(dups$client_id) == 0) {
  cat("None\n")
} else {
  cat(dups$client_id, "\n")
}

```


\newpage
## Process Table 1: 7 days since first contact and no consent call
```{r Table 1: 7 days since first contact and no consent call}

# tracker: date of 1st SMS (track_first_text_date) & (track_consent_call) yes/no
screen <- screen %>%
  mutate(track_first_text_date = as.Date(track_first_text_date),
    sms7 = ifelse(last_friday - track_first_text_date >=7,1,0),
         noconsent = ifelse((is.na(track_consent_call) | track_consent_call == 0) & sms7 == 1 & (call_interest == 1 | is.na(call_interest)), 1, 0)

         )

tbl1 <- screen %>%
  summarise(
    "Screened >=7days ago" = sum(sms7, na.rm = T),
    "No consent call" = sum(noconsent,na.rm = T)
  )

kbl(tbl1, booktabs=T) 

```

## IDs of pending calls
```
IDs: `r screen$client_id[screen$noconsent==1 & !is.na(screen$sms7)]`

```

## Process Table 2: Finished baseline but didn’t install FOCUS after 30 days
```{r Table 2: Finished baseline but didn’t install FOCUS after 30 days}

# assessment: redcap completed timestamp field for last survey (probably GAD); (track_treatment_start) date non-null
assess <- assess %>%
  mutate(gad7_a7c3_date = as.Date(substr(gad7_a7c3_timestamp,start=1, stop=10)),
    baseline30 = ifelse(redcap_event_name=="client_baseline_arm_1" & (last_friday - gad7_a7c3_date >=30) ,1,0),
    nostart = ifelse(track_treatment_start=="" & baseline30==1, 1, 0)
         )

tbl2 <- assess %>%
  summarise(
    "Completed baseline >=30 days ago" = sum(baseline30, na.rm = T),
    "No treatment start date" = sum(nostart,na.rm = T)
  )

kbl(tbl2, booktabs=T) 

```

## Process Table 3: 97 days since treatment start but no 3M survey response
```{r Table 3: 97 days since treatment start but no 3M survey response}

# assessment: redcap completed timestamp field for last survey at 3M (probably GAD) is null; (track_treatment_start) date >97 days
assess <- assess %>%
  mutate(track_treatment_start = as.Date(track_treatment_start),
    sincestart97 = ifelse(last_friday - track_treatment_start >=97 ,1,0),
    nofu = ifelse(redcap_event_name=="client_3m_arm_1" & is.na(gad7_a7c3_date) & sincestart97==1, 1, 0)
         )

tbl3 <- assess %>%
  summarise(
    "Started treatment >=97 days ago" = sum(sincestart97, na.rm = T),
    "No 3M" = sum(nostart,na.rm = T)
  )

kbl(tbl3, booktabs=T) 

```